\history{HEAD}{\mmCEsimDate}[https://github.com/mmcesim/mmcesim]
\subsection*{New Features}
\begin{itemize}
  \item ALG library enhancement (\GHhash{49}, \GHhash[pull]{51}):
  \begin{itemize}
    \item Add OMPL \cite{zhao2023ompl} algorithm to the library.
    \item ALG dependency check.
    \item Enhanced log and \TeX{} report (\GHhash[pull]{55}).
  \end{itemize}
  \item Update Doxygen website configurations (including more graphs).
\end{itemize}
\subsection*{Bug Fixes}
\begin{itemize}
  \item Rename configuration file to \texttt{mmcesim.cfg} (\GHhash{50}, \GHhash[pull]{53}).
  \item Fix C++ (Armadillo) runtime error when simulating with \texttt{-O2} or \texttt{-O3} on macOS by patching \texttt{arma::randperm} (\GHhash{52}, \GHhash[pull]{54}).
\end{itemize}
\subsection*{News}
\begin{itemize}
  \item The research paper entitled `Beam Pattern and Reflection Pattern Design for Channel Estimation in RIS-assisted mmWave MIMO Systems' \cite{you2023beam} has been accepted by \textsc{IEEE Transactions on Vehicular Technology} (May~21, 2023);
  \item The research paper entitled `OMPL-SBL Algorithm for Intelligent Reflecting Surface-Aided mmWave Channel Estimation' \cite{zhao2023ompl} is online as an early access paper of \textsc{IEEE Transactions on Vehicular Technology} (Jun.~27, 2023): \url{https://ieeexplore.ieee.org/abstract/document/10164645} (\GHhash[discussions]{69}).
\end{itemize}

\history{v0.2.1}{2023/03/31}
\subsection*{New Features}
\begin{itemize}
  \item Colorful terminal (\GHhash{22}).
  \item \texttt{mmcesim-maintain} tool support (\GHhash{25}).
  \item Log system support with cleaner terminal output (\GHhash{32}, \GHhash[pull]{36}).
  \item \texttt{mmcesim-log} tool support (\GHhash{37}, \GHhash[pull]{39}, \GHhash[pull]{47}).
  \item Support \texttt{NO\_COLOR}\indextt{NO\_COLOR} standard (\GHhash{42}, \GHhash[pull]{48}).
  \item Syntax highlight for ALG language on \href{https://mmcesim.org}{mmcesim.org} with a custom lexer (\GHhash[issues][mmcesim.org]{1}).
\end{itemize}
\subsection*{Bug Fixes}
\begin{itemize}
  \item Fix the Docker \texttt{entrypoint} command.
  \item Fix \textit{total lines} badge display in README (\GHhash{40}, \GHhash[pull]{41}).
  \item Fix Ubuntu 20 release error (\GHhash{46}).
\end{itemize}
\subsection*{News}
\begin{itemize}
  \item Short domain \href{https://mmces.im}{mmces.im} has been registered alongside \href{https://mmcesim.org}{mmcesim.org} (\GHhash[discussions]{43}).
\end{itemize}

\history{v0.2.0}{2023/01/20}
\subsection*{New Features}
\begin{itemize}
  \item Active beam pattern design support (\GHhash{18}).
  \item Report generation of RIS-assisted systems (\GHhash{3}).
\end{itemize}
\subsection*{Bug Fixes}
\begin{itemize}
  \item Fix inconsistency of \LaTeX{} report destination directory.
\end{itemize}
\subsection*{News}
\begin{itemize}
  \item The research paper entitled `OMPL-SBL Algorithm for Intelligent Reflecting Surface-Aided mmWave Channel Estimation' \cite{zhao2023ompl} has been accepted by \textsc{IEEE Transactions on Vehicular Technology} (Jan.~13, 2023).
\end{itemize}

\history{v0.1.1}{2023/01/11}
\subsection*{New Features}
\begin{itemize}
  \item Multi RIS assisted systems support (\GHhash{3});
  \item RIS pattern design support (\GHhash{17}).
\end{itemize}
\subsection*{Bug Fixes}
\begin{itemize}
  \item Fix \texttt{cmake install} configurations.
\end{itemize}
\subsection*{News}
\begin{itemize}
  \item Automated release process with a better CI workflow (\GHhash{20}).
\end{itemize}

\history{v0.1.0}{2022/10/16}
\subsection*{New Features}
\begin{itemize}
  \item Basic mmWave MIMO systems channel estimation support;
  \item Design of ALG language;
  \item Export of code with Armadillo library;
  \item Auto simulation (\GHhash{5}).
\end{itemize}

\history{v0.0.1}{2022/07/27}
Though the app has not been fully developed,
the task-oriented concept has already been established.

% \section*{Start of The Project\IndexDotfill\normalfont\textsf{\textcolor{forestgreen}{2022/05/31}}}
